---
title: "Draft Quarto document"
author: "Sofie H. G. Jakobsen"
format: html
---

## Header 1

```{r setup}

library(tidyverse)
library(here)
#library(snakecase)
source(here("R/functions.R"))
```



## Import new data
```{r, eval=FALSE}

# Read file

here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |> # Here stays in our project. #pipe command/shift/m
  read_csv(show_col_types = FALSE,  #Remove the guessing from the read_csv function
           name_repair = to_snake_case, #make it snake_case, under scroll between each word 
           n_max = 100) #we use the _ type and not . cuz it is in the tidyverse package. 

```

## Exercise: Reading other files.
 15.6 🧑‍💻 Exercise: Read in other data files

```{r, eval=FALSE}

#5C - HR
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(show_col_types = FALSE,
           name_repair= to_snake_case)

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
   read_csv(show_col_types = FALSE,  #Remove the guessing from the read_csv function
           name_repair = to_snake_case, #make it snake_case, under scroll between each word 
           n_max = 100)



#6b - eda
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
  read_csv(show_col_types = FALSE,
           name_repair= to_snake_case)

here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
   read_csv(show_col_types = FALSE,  #Remove the guessing from the read_csv function
           name_repair = to_snake_case, #make it snake_case, under scroll between each word 
           n_max = 100)


# > styler:::style_active_file()
```


# Learn how to make functions!
Everything in R is an object.
some objects can preform an action which makes them a function.
normally functions can be regonized by the () at theor end. 
some functions do not have a () examples are <-, +, - ect. 

A function is normally build like this:
```{r, eval=FALSE}

name <- function(argument1, argument2) {
  # body of function
  output <- ...
  return(output)
}

```

The function needs a name, arguments eg a data frame. the we add the body of the function which corrspond to what the function should do. 
the last part is a return argument which gives us the results of the function


## Create our own function

make a function that can add two numbers together
Option-shift-() = {}
```{r, eval=FALSE}
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}


```


add a roxygen skeleton to the function (insert a roxygen for you function (command-shift-p = roxyge, it should show up))
```{r, eval=FALSE}
#' Title: Add two numbers together.
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers.
#' @export # Mainly used for packages so delete it 
#'
#' @examples also if u create a package to provide an example of how it is used
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}


```


Now we learn to use a function in pratice for importin all the files
check function name by writing ?function name and it will let u know if there ar eno functions witht this name
```{r, eval=FALSE}

#' Read in one nurses' stress data file
#'
#' @param file_path A path to a data file
#'
#' @returns output a data frame / tibble
read <- function(file_path) {
  data <- file_path |>
   read_csv(show_col_types = FALSE,  
           name_repair = to_snake_case, 
           n_max = 100
   )
  return(data)
  }


```

```{r, eval=FALSE}

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |> 
  read()



```



```{r, eval=FALSE}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |> 
  read()

```

 16.7 🧑‍💻 Exercise: Add another function argument to read different number of rows

```{r, eval=FALSE}

#' Read in one nurses' stress data file
#'
#' @param file_path A path to a data file
#' @param max_rows The number of rows of the data file the should be imported, standard is 100 unless antoher value is choosen  
#'
#' @returns output a data frame / tibble
read <- function(file_path, max_rows = 100) {
  data <- file_path |>
   read_csv(show_col_types = FALSE,  
           name_repair = to_snake_case, 
           n_max = max_rows
   )
  return(data)
  }

```



```{r, eval=FALSE}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```
pak::pak() #installs all packages the project is dependednt on


###Updating the function so it uses the right packages 
```{r, eval=FALSE}
#' Read in one nurses' stress data file.
#'
#' @param file_path Path to the data file.
#' @param max_rows Maximum number of rows to read.
#'
#' @returns Outputs a data frame/tibble.
#'
read <- function(file_path, max_rows = 100) {
  data <- file_path |>
   readr::read_csv(show_col_types = FALSE,  
           name_repair = snakecase::to_snake_case, 
           n_max = max_rows
   )
  return(data)
  }
```


