---
title: "Draft Quarto document"
author: "Sofie H. G. Jakobsen"
format: html
---

# Intermediate reproducible Research in R

```{r setup}

library(tidyverse)
library(here)
#library(snakecase) # only used for read function which is now in the function documet
library(fs)
source(here("R/functions.R"))
```



## 15 Pre-process data as you import it

### Import new data
```{r, eval=FALSE}

# Read file

here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |> # Here stays in our project. #pipe command/shift/m
  read_csv(show_col_types = FALSE,  #Remove the guessing from the read_csv function
           name_repair = to_snake_case, #make it snake_case, under scroll between each word 
           n_max = 100) #we use the _ type and not . cuz it is in the tidyverse package. 

```


### 15.6 🧑‍💻 Exercise: Read in other data files

```{r, eval=FALSE}

#5C - HR
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(show_col_types = FALSE,
           name_repair= to_snake_case)

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
   read_csv(show_col_types = FALSE,  #Remove the guessing from the read_csv function
           name_repair = to_snake_case, #make it snake_case, under scroll between each word 
           n_max = 100)



#6b - eda
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
  read_csv(show_col_types = FALSE,
           name_repair= to_snake_case)

here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") |>
   read_csv(show_col_types = FALSE,  #Remove the guessing from the read_csv function
           name_repair = to_snake_case, #make it snake_case, under scroll between each word 
           n_max = 100)


# > styler:::style_active_file()
```


# 16  Bundling code into functions
Everything in R is an object.
some objects can preform an action which makes them a function.
normally functions can be regonized by the () at theor end. 
some functions do not have a () examples are <-, +, - ect. 

A function is normally build like this:
```{r, eval=FALSE}

name <- function(argument1, argument2) {
  # body of function
  output <- ...
  return(output)
}

```

The function needs a name, arguments eg a data frame. the we add the body of the function which corrspond to what the function should do. 
the last part is a return argument which gives us the results of the function


## Create our own function

make a function that can add two numbers together
Option-shift-() = {}
```{r, eval=FALSE}
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}


```

### roxygen
add a roxygen skeleton to the function (insert a roxygen for you function (command-shift-p = roxyge, it should show up))
```{r, eval=FALSE}
#' Title: Add two numbers together.
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers.
#' @export # Mainly used for packages so delete it 
#'
#' @examples also if u create a package to provide an example of how it is used
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}


```


Now we learn to use a function in pratice for importin all the files
check function name by writing ?function name and it will let u know if there ar eno functions witht this name
```{r, eval=FALSE}

#' Read in one nurses' stress data file
#'
#' @param file_path A path to a data file
#'
#' @returns output a data frame / tibble
read <- function(file_path) {
  data <- file_path |>
   read_csv(show_col_types = FALSE,  
           name_repair = to_snake_case, 
           n_max = 100
   )
  return(data)
  }


```

```{r, eval=FALSE}

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |> 
  read()



```



```{r, eval=FALSE}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |> 
  read()

```

### 16.7 🧑‍💻 Exercise: Add another function argument to read different number of rows

```{r, eval=FALSE}

#' Read in one nurses' stress data file
#'
#' @param file_path A path to a data file
#' @param max_rows The number of rows of the data file the should be imported, standard is 100 unless antoher value is choosen  
#'
#' @returns output a data frame / tibble
read <- function(file_path, max_rows = 100) {
  data <- file_path |>
   read_csv(show_col_types = FALSE,  
           name_repair = to_snake_case, 
           n_max = max_rows
   )
  return(data)
  }

```



```{r, eval=FALSE}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

# 17  Making robust and reusable functions
pak::pak() #installs all packages the project is dependednt on


### Updating the function so it uses the right packages 
```{r, eval=FALSE}
#' Read in one nurses' stress data file.
#'
#' @param file_path Path to the data file.
#' @param max_rows Maximum number of rows to read.
#'
#' @returns Outputs a data frame/tibble.
#'
read <- function(file_path, max_rows = 100) {
  data <- file_path |>
   readr::read_csv(show_col_types = FALSE,  
           name_repair = snakecase::to_snake_case, 
           n_max = max_rows
   )
  return(data)
  }
```

# Day 2
# 18  Doing many things at once with functionals

## How to load more than one file?

### Using map()
we will use: 
dir_ls() - directory that lists all files. recurse looks in all the subfolder, regexp is for the next session. This function is in the fs packages.
This kinda genereate our vector like the description form the reading excersice. 
```{r}


hr_files <- here("data-raw/nurses-stress/") |> #pipe the first argument 
  fs::dir_ls(regexp = "HR.csv.gz",
         recurse = TRUE) # it will look in all the subfolders and it is looking for HR.csv.gz files in nurses-stress

# add it into the map function

###hr_data <- hr_files |> 
###  purrr::map(read)

#hr_data

# we now want to combine the code (building the code form before)
###hr_data <- hr_files |> 
###  purrr::map(read) |>
###  purrr::list_rbind()

#remeber to add purrr usethis::use_package("purrr")
#add id
hr_data <- hr_files |> 
  purrr::map(read) |>
  purrr::list_rbind(names_to = "file_path_id") 
#this id is horrible.. next session will change this 

```

### 18.5 🧑‍💻 Exercise: Convert the map with reading code into a function

```{r, eval = FALSE}
#' Read in all files in the nurse-stress folder
#'
#' @param file_name the name or type of data that needs to be loaded.  
#'
#' @returns Dataframe with a Id, collectioin time and the data point ef hr. 

read_all <- function(file_name) {
  # Code that does something
  hr_files <- here::here("data-raw/nurses-stress/") |> #pipe the first argument 
  fs::dir_ls(regexp = file_name,
         recurse = TRUE)

  hr_data <- hr_files |> 
  purrr::map(read) |>
  purrr::list_rbind(names_to = "file_path_id") 

  return(hr_data)
}

# this function was moved to functions.R 

```


```{r}


hr_data <- read_all("HR.csv.gz")
ibi_data <- read_all("IBI.csv.gz")
bvp_data <- read_all("BVP.csv.gz")
```



### 18.6 🧑‍💻 Extra exercise: Include a new max_rows argument to read_all()'
```{r, eval = FALSE}
#' Read in all files in the nurse-stress folder
#'
#' @param file the name or type of data that needs to be loaded.  
#'
#' @returns Dataframe with a Id, collectioin time and the data point ef hr. 

read_all <- function(file, max_rows = 100) {
  # Code that does something
  hr_files <- here::here("data-raw/nurses-stress/") |> #pipe the first argument 
  fs::dir_ls(regexp = file,
         recurse = TRUE)

  hr_data <- hr_files |> 
  purrr::map(\(file) read(file, max_rows = max_rows)) |> 
  purrr::list_rbind(names_to = "files_path_id") 

  return(hr_data)
}

# this function was moved to functions.R 

read_all("HR.csv.gz", max_rows = 1000)
read_all("HR.csv.gz", max_rows = 10)
read_all("HR.csv.gz", max_rows = Inf)

```


```{r}
read_all("HR.csv.gz", max_rows = 1000)
read_all("HR.csv.gz", max_rows = 10)
read_all("HR.csv.gz", max_rows = Inf)
```



### 18.7 🧑‍💻 Extra exercise: Move the here::here() path out of the function
Se funktions dokumentet here er det opdateret så man kan ændre path... det virker ikke.... til næste opgave. 

# 19 Processing strings with regular expressions
### 19.2 🧑‍💻 Exercise: Inspect and compare the data frames



```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here::here("data-raw/nurses-stress/survey-results.csv.gz") |>
 read()


hr_data
survey_data
```

### extract the ID

```{r}

hr_data |> 
  mutate(
    id = str_extract(
      file_path_id, 
      pattern = "/stress/[:alnum:]{2}/"
    ) |> 
      str_remove("/stress/") |>  #stress is important to include cuz it really specefies. 
      str_remove("/"), #remove the stress so we only get the id
    .before = file_path_id # how to organice the coloums 
  ) |> 
  select(-file_path_id)


```



### 19.7 🧑‍💻 Exercise: Convert ‘get ID’ code into a function

```{r}
#' extract IDs from the data frame
#'
#' @param data the data frame from which we want to modify the id so it can be merged
#'
#' @returns a dataframe with the new ids
get_participant_id <- function(data){
  data_with_id <- data |> 
  mutate(
    id = str_extract(
      file_path_id, 
      pattern = "/stress/[:alnum:]{2}/"
    ) |> 
      str_remove("/stress/") |>  #stress is important to include cuz it really specefies. 
      str_remove("/"), #remove the stress so we only get the id
    .before = file_path_id # how to organice the coloums 
  ) |> 
  select(-file_path_id)
  return(data_with_id)
}

get_participant_id(hr_data)

```



### 19.8 🧑‍💻 Extra exercise: Simplify the regex with look arounds
```{r}
#' Extract Id form the file_path_id
#'
#' @param data the coloum that ocntains the ID we would like to extract 
#'
#' @returns the data frame with the new id coloum containing the ids with two alnum, where the file_path_ide is removed

get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        "(?<=/stress/)[:alnum:]{2}(?=/)" #?<= this means that it should look for this /stress/ to stand before the id [:alnum:]{2} that we arw looking for and from the following ?=/ is to remove or look for the id/ but not include the /.
      ),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)
  return(data_with_id)
}

get_participant_id(hr_data)
```

# 20  Using split-apply-combine to help in processing


